Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
small space adjustment
small fixes
add sentence about new collaborators

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Software Foundations~\cite{SF} & 2007 & Executable\\
  Certified Programming with Dependent Types~\cite{chlipalacpdt2011} & 2011 &  Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  Programs and Proofs~\cite{Sergey:PnP} & 2014 & Executable\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Computer Arithmetic and Formal Proofs~\cite{Boldo2017} & 2017 & Traditional\\
  Mathematical Components~\cite{MCB} & 2018 & Traditional\\
  \hline
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:books}
\end{table}

@@

Due to our reliance on LaTeX for writing the book, obtaining a book representation in HTML is more cumbersome than for executable books such as Software Foundations~\cite{SF} and Certified Programming with Dependent Types~\cite{chlipalacpdt2011}. Currently, we generate the Coq code documentation as HTML separately from the book.

@@

We plan to extend \Hydras in two main directions. Firstly, we plan to build a bridge between the combinatorial results of \Hydras and the set-theoretic content of \gaia, and make possible the transfer of many interesting theorems between the two packages. Secondly, we aim to write a formal proof in \coq of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.

\Hydras is not limited to the study of ordinal numbers and applications.
For instance, we are also developing  a module about efficient exponentiation
algorithms, and hope to extend our project to new topics.

>>>>

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Software Foundations~\cite{SF} & 2007 & Executable\\
  Certified Programming with Dependent Types~\cite{chlipalacpdt2011} & 2011 &  Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  Programs and Proofs~\cite{Sergey:PnP} & 2014 & Executable\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Computer Arithmetic and Formal Proofs~\cite{Boldo2017} & 2017 & Traditional\\
  Mathematical Components~\cite{MCB} & 2018 & Traditional\\
  \hline
  \end{tabular}
  \caption{Coq book categorization.}
  \label{tbl:books}
\end{table}

@@

Due to our reliance on LaTeX for writing the book, obtaining a book representation in HTML is more cumbersome than for executable books such as Software Foundations~\cite{SF} and Certified Programming with Dependent Types~\cite{chlipalacpdt2011}. Currently, we generate the Coq code documentation in HTML form separately from the book.

@@

We plan to extend \Hydras in two main directions. Firstly, we plan to bridge the combinatorial results of \Hydras and the set-theoretic content of \gaia, enabling the transfer of many interesting theorems between the two packages. Secondly, we aim to write a formal proof in \coq of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.
%
Moreover, \Hydras is not limited to the study of ordinal numbers and applications.
We are also developing a package about efficient exponentiation
algorithms, and aim to eventually include new topics. We invite new collaborators to join us in our efforts.
